A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.Rnw
More bib

Using a peer to peer approach, the SPACE framework \cite{Leclerc2016} distributes fitness 
evaluations across a heterogeneous pool of cloud compute nodes and volunteer
peer computers running a browser. In SPACE peers stablis a bi-directional 
communication with the server using the Socket.io JavaScript library.  
As an experiment they provide an ASM.js compiled version of the RoboGen 
software platform, showing that JavaScript can be used in a broad 
spectrum of applications.

>>>>

Using a peer to peer approach, the SPACE framework \cite{leclerc2016seamless} distributes fitness 
evaluations across a heterogeneous pool of cloud compute nodes and volunteer
peer computers running a browser. In SPACE peers stablis a bi-directional 
communication with the server using the Socket.io JavaScript library.  
As an experiment they provide an ASM.js compiled version of the RoboGen 
software platform, showing that JavaScript can be used in a broad 
spectrum of applications.
